Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-08 paperIEEE.tex
typo, clarification
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@115 db7c848b-7755-4df2-b763-8796797afa52

This figure gives an impression of how individual modes perform on heterogeneous
systems. In this case the tree equalizer performs best (\fig{fEqualizers}
(left)), as it allows us to a priori define how much {\em usage} it should make
of individual nodes, i.e., bias the allocation of rendering time in accordance
with the (simulated) compute resources. \fig{fEqualizers} (right), on the other
hand, illustrates how the tested decomposition modes perform on a system where
compute resources fluctuate randomly every frame, as can arguably be the case
for virutalized enviroments. For this scenario tile equalizer seems best suited,
as it performs load balancing implicitly and does not assume coherence of
available resources between frames. The simpler tree equalizer also outperforms
the load equalizer in this experiment.

@@

The data distribution benchmarks have been performed on a cluster using
dual processor Intel Xeon X5690 CPUs (3.47\,GHz), 24\,GB main memory, 10\,GBit/s
Ethernet and QDR Infiniband. Intel ICC 2017 has been used with CMake 3.2 release
mode settings to compile the software stack.

>>>>

This figure gives an impression of how individual modes perform on heterogeneous
systems. In this case the tree equalizer performs best (\fig{fEqualizers}
(left)), as it allows us to a priori define how much {\em usage} it should make
of individual nodes, i.e., bias the allocation of rendering time in accordance
with the (simulated) compute resources. \fig{fEqualizers} (right), on the other
hand, illustrates how the tested decomposition modes perform on a system where
compute resources fluctuate randomly every frame, as can arguably be the case
for virtualized enviroments. For this scenario tile equalizer seems best suited,
as it performs load balancing implicitly and does not assume coherence of
available resources between frames. The simpler tree equalizer also outperforms
the load equalizer in this experiment.

@@

The data distribution benchmarks have been performed on a cluster using
dual processor Intel Xeon X5690 CPUs (3.47\,GHz), 24\,GB main memory per node, 10\,GBit/s
Ethernet and QDR Infiniband. Intel ICC 2017 has been used with CMake 3.2 release
mode settings to compile the software stack.
